\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}

\title{Fuzzer for Dart}
\author{Waleed Khan Jadoon}
\date{June 2026}

\begin{document}

\maketitle

\section{Introduction}

A report on a novel fuzzer for dart.

\section{Goals of the Seminar}

\begin{enumerate}
    \item What is your programming language?
    \begin{enumerate}
        \item What's the ecosystem like?
        \item Is it statically or dynamically typed?
        \item What's so special about it?
        \item Provide a general background.
    \end{enumerate}

    \item Where did you source your grammar? (e.g. ANTLR Grammar converted to fandango)

    \item At a high-level, what features of the grammar did you remove for your more reasonable subset?
    \begin{enumerate}
        \item If you kept a detailed list, including that as a document alongside the report is good.
    \end{enumerate}

    \item What constraints did you add?
    \begin{enumerate}
        \item What were some of the most common errors you encountered when generating programs without constraints?
        \item What did correct, constrained programs look like?
        \item Did goals make generation infeasible?
    \end{enumerate}

    \item Once you have the above three experiments running, what are your overall impressions of the results?
\end{enumerate}

\section{Additional Notes}
Work In Progress. \href{https://www.overleaf.com/project/6a2b2e1e30622bf77d5cecee}{Link to Overleaf document}

\end{document}
